Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-09-16 paper/changes.tex
Addressed reviewer's comments

\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage[colorlinks=true]{hyperref}
\title{Handling of Rejected Papers
Changes after the last submission}
\begin{document}
\date{}
\maketitle

@@

 \begin{itemize}
  \item {Machine Learning}

@@

  Another avenue for using deep-networks \textit{within} our current
  work is to replace the currently used fixed eigenspace provided by
  PCA by a learnt feature basis provided by a network such as an
  autoencoder. For each dataset, an autoencoder may be trained to
  learn a specific set of latent features (this might again require
  atleast a few tens of volumes). We see this as a future direction of
  work.
\end{itemize}

>>>>

\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Response to Reviewers and Associate Editor}
\begin{document}
\date{}
\maketitle

@@

 \begin{itemize}
  \item \textbf{Machine Learning}

@@

  Another avenue for using deep-networks \textit{within} our current
  work is to replace the currently used fixed eigenspace provided by
  PCA by a learnt feature basis provided by a network such as an
  autoencoder. For each dataset, an autoencoder may be trained to
  learn a specific set of latent features (this might again require
  atleast a few tens of volumes). We see this as a future direction of
  work.

\item \textbf{Details of other methods used for comparison}
 We have compared our method with Algebraic Reconstruction Technique
 (ART), Simultaneous Algebraic Reconstruction Technique (SART),
 Simultaneous Iterative Reconstruction Technique (SIRT), Total
 Variation (TV) and Compressed Sensing (CS) with Haar wavelet and DCT
 as sparsity basis. The details of solvers used for these
 algorithms are now mentioned in Page.~7 (Section-6A). For CS
 reconstruction, we observed that Haar wavelet and DCT were best
 suited for our dataset among various other possible sparsity basis.

\item \textbf{Discussion about Metrics used}
  In our experiments, we observed that for a given dataset and a set of projection measurements, the intensity span of histograms of reconstructed volumes differ across various methods and solvers. Hence, we choose to focus on preserving the structures on our reconstructions, and not rely on the absolute intensity values alone. Hence, we choose SSIM with a higher weightage to structure-preservation. For our record, we have computed RMSE values as well and they are presented here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.

\begin{table}[!h]
  \centering
 \caption{RMSE within the RoI of 3D reconstructed Potato volume from various
    methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline 
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline  0.29 & 0.24 & \textcolor{red}{0.18}
\\ \hline
\end{tabular}
\label{table:potato_rmse}
\end{table}

\begin{table}[!h]
  \centering
 \caption{RMSE within the RoI of 3D reconstructed Sprouts volume from various
    methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline 
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline  0.53 & 0.48 & \textcolor{red}{0.30}
\\ \hline
\end{tabular}
\label{table:sprouts_rmse}
\end{table}

\item \textbf{Dicsussion about Computational Cost}\\
  We now present details of both time and space complexities of our technique in Section.7B of our paper.
\end{itemize}

### 2021-09-16 paper/post_tci.tex
Addressed reviewer's comments

The changes and new structures present in the test data will generate
different artifacts for different reconstruction techniques. These
artifacts would not be captured by reconstructions of the object-prior
since the underlying new changes and structures may be absent in all
of the previously scanned objects. We aim to let the weights be
independent of the type of artifact. Hence, we use a combination of
different reconstruction techniques to generate different types of
eigenspaces and combine information from all of them to compute
weights. To illustrate the benefit of this method, we first performed
2D reconstruction of a test slice from the potato dataset.
Fig.~\ref{fig:potato_data_2D} shows the test and template
slices. Fig.~\ref{fig:weights_map_2Dpotato} shows the weights-maps
generated using Eq.~\ref{eq:weightsEq} by various reconstruction
methods. It can be seen that the weights are low in the region of the
new change in test data. Because all the iterative methods are
computationally expensive, we chose only FBP and TV for
computing weights-maps for all 3D reconstructions.
%---------------------------------------

@@

\section{Discussion}
\label{sec:discussion}
In this section, we discuss tuning of the parameters
used in our method. $\lambda_1$, $\lambda_2$ and $k$ are the three
hyper-parameters that need to be chosen carefully for optimal
reconstruction. In our experiments, $\lambda_1$ was tuned to maximize
SSIM of the whole reconstructed test volume for TV reconstruction of
each dataset. This value was retained for spatially-varying
prior-based reconstruction as well. The value of $\lambda_2$ largely
depends on the amount of artefacts we aim to remove by using
object-prior at the cost of their dominance in the new regions. This
value was chosen to lie between $0-3$ for our datasets. Finally, the
hyper-parameter $k$ defines the sensitivity of the weights map to the
difference between test image and object-prior (projection of
test onto the space of object-prior). When $k=0$, our method 
behaves similar to the reconstruction using TV-only regularization. As $k$ increases, the weights map starts
capturing new changes in the test, at the cost of detecting a few
false positives i.e., false new changes. In other words, as the
weights-map becomes more sensitive to the difference between the test
and object-prior, it becomes more noisy. In order to visualize the
effect of the hyper-parameter $k$, we performed 2D reconstructions on
okra dataset for different values of
$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
obtained for each of the $k$ values and
Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
final reconstructions. We run our experiments for a few values of $k$
and choose the best reconstruction based on our tolerance for noise
in the weights-map.
When a large number of templates are available, this parameter can be
chosen by assuming one of the templates as test and choosing the $k$
that gave the best reconstruction. Alternatively, in cases where one
wishes to completely avoid the use of this hyper-parameter, one can
construct a binary weights-map using a learning based method described
in the supplementary material~\cite{supp_paper}.

@@

>>>>

The changes and new structures present in the test data will generate
different artifacts for different reconstruction techniques. These
artifacts would not be captured by reconstructions of the object-prior
since the underlying new changes and structures may be absent in all
of the previously scanned objects. We aim to let the weights be
independent of the type of artifact. Hence, we use a combination of
different reconstruction techniques to generate different types of
eigenspaces and combine information from all of them to compute the
weights map. To illustrate the benefit of this method, we first performed
2D reconstruction of a test slice from the potato dataset using
various reconstruction methods. We used implementations of algebraic
methods such as ART, SIRT and SART from~\cite{AIR_tools} and
implementations of CS solver from~\cite{l1ls}. Among various possible
sparsity basis for CS reconstruction, we observed that Haar wavelets
and DCT were best suited for this
dataset. Fig.~\ref{fig:potato_data_2D} shows the test and template
slices and Fig.~\ref{fig:weights_map_2Dpotato} shows the weights maps
generated using Eq.~\ref{eq:weightsEq} by various reconstruction
methods. It can be seen that the weights are low in the region of the
new change in test data. Because all the iterative methods are
computationally expensive, we chose only FBP and TV for computing
weights-maps for all 3D reconstructions.
%---------------------------------------

@@

\section{Discussion}
\label{sec:discussion}
In this section, we discuss tuning of parameters and the computational complexity of our method.
\subsection{Tuning of parameters:}
$\lambda_1$, $\lambda_2$ and $k$ are the three
hyper-parameters that need to be chosen carefully for optimal
reconstruction. In our experiments, $\lambda_1$ was tuned to maximize
SSIM of the whole reconstructed test volume for TV reconstruction of
each dataset. This value was retained for spatially-varying
prior-based reconstruction as well. The value of $\lambda_2$ largely
depends on the amount of artefacts we aim to remove by using
object-prior at the cost of their dominance in the new regions. This
value was chosen to lie between $0-3$ for our datasets. Finally, the
hyper-parameter $k$ defines the sensitivity of the weights map to the
difference between test image and object-prior (projection of
test onto the space of object-prior). When $k=0$, our method 
behaves similar to the reconstruction using TV-only regularization. As $k$ increases, the weights map starts
capturing new changes in the test, at the cost of detecting a few
false positives i.e., false new changes. In other words, as the
weights-map becomes more sensitive to the difference between the test
and object-prior, it becomes more noisy. In order to visualize the
effect of the hyper-parameter $k$, we performed 2D reconstructions on
okra dataset for different values of
$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
obtained for each of the $k$ values and
Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
final reconstructions. We run our experiments for a few values of $k$
and choose the best reconstruction based on our tolerance for noise
in the weights-map.
When a large number of templates are available, this parameter can be
chosen by assuming one of the templates as test and choosing the $k$
that gave the best reconstruction. Alternatively, in cases where one
wishes to completely avoid the use of this hyper-parameter, one can
construct a binary weights-map using a learning based method described
in the supplementary material~\cite{supp_paper}.

@@

\subsection{Computational Complexity:}
The use of object-priors does introduce additional time and space complexities when compared to the use of a simpler prior such as TV-only prior.  For spatially-varying prior, most of the
computation time is used in the generation of low quality eigen-space
by reconstructing each of the templates using TV and FDK. If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored, in order to save computational costs. If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent. Here below, we describe the
time complexity of spatially-varying prior technique.  If
\begin{itemize}
\item $N =$ number of voxels of the volume
\item $T =$ number of templates available, and
\item $F =$ time taken for iterative TV optimization,
\end{itemize}
then, the computational complexity is sum of the following
\begin{itemize}
\item $O(NT^2+T^3)$ for creating the eigenspace,
\item $O(NT^2)$ for deriving the weights map, and
\item time $F$  taken for iterative minimization
\end{itemize}
where $O(.)$ is the notation for `Big O' used in complexity analysis. In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions. We need to store a single weights map volume regardless of the number of templates available.
